Equilibria and Convergence of Fictitious Play\\ on Network Aggregative Games

### 2021-05-28 Documents/FP in NAGs/neurips_2021.tex
various edits
Final Updates

  \begin{assumption}\label{ass::rowstochastic}
    The weighted adjacency matrix $\weightset$ is constant and
    \emph{row stochastic} meaning that the sum \fb{of} elements in each row of
    $\weightset$ is equal to one. This assumption is made to ensure
    that the analysis of NA games can be derived as a natural
    extension of the classic setting of two-player games. We can
    think of the row stochastic condition as the ability of each agent
    to prioritise the state information it receives from each of its
    neighbours. It is also a standard assumption made in the analysis
    of networks and is straightforward to implement \cite{Mai2019}.
  \end{assumption}

@@

  \begin{assumption}\label{ass::sameactions}
    The cardinality of each action set $|\actionset{\mu}|$ is equal
    for all agents. This is another standard assumption that is made in
    most game0theoretic settings and includes \fb{?}, as a special
    case. However, it should be noted that, in \cite{Ewerhart2020},
    CTFP is analysed without this assumption.
  \end{assumption}

>>>>

  \begin{assumption}\label{ass::rowstochastic}
    The weighted adjacency matrix $\weightset$ is constant and
    \emph{row stochastic} meaning that the sum of elements in each row of
    $\weightset$ is equal to one. This assumption is made to ensure
    that the analysis of NA games can be derived as a natural
    extension of the classic setting of two-player games. We can
    think of the row stochastic condition as the ability of each agent
    to prioritise the state information it receives from each of its
    neighbours. It is also a standard assumption made in the analysis
    of networks and is straightforward to implement \cite{Mai2019}.
  \end{assumption}

@@

  \begin{assumption}\label{ass::sameactions}
    The cardinality of each action set $|\actionset{\mu}|$ is equal
    for all agents. This is another standard assumption that is made in
    most game-theoretic settings. However, it should be noted that, in \cite{Ewerhart2020},
    CTFP is analysed without this assumption.
  \end{assumption}
